The Name of the Title Is Hope

### 2024-04-08 paper/paper.tex
paper and removed locate

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), Sigma protocols remain a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol and 
its $n$ NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems  (\textbf{Berry: does it sound okay?}), 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.

>>>>

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), Sigma protocols remain a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems, 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.
